Interactive Visual Analysis of Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-12-16 draft.tex
references results figure in the text; revised acknowledgements

The upper scatter plot shows the results for all variables, either metrics expressed via their quantiles, or categorical.

@@

The lower scatter plot displays the dummy variables derived from the original variables.

@@

@@

\noindent SHIP is part of the Community Medicine Research net of the University of Greifswald, Germany, which is funded by the Federal Ministry of Education and Research (grant no. 03ZIK012), the Ministry of Cultural Affairs as well as the Social Ministry of the Federal State of Mecklenburg-West Pomerania. Whole-body MR imaging was supported by a joint grant from Siemens Healthcare, Erlangen, Germany and the Federal State of Mecklenburg-Vorpommern. The University of Greifswald is a member of the ‘Centre of Knowledge Interchange’ program of the Siemens AG. This work was supported by the DFG Priority Program 1335: Scalable Visual Analytics. The work was partly funded by the German Ministry of Education and Research (BMBF) within the STIMULATE project (grant no. 03FO16101A).

>>>>

The upper plot shows the results for all variables, either metrics expressed via their quantiles, or categorical.

@@

The lower plot displays the dummy variables derived from the original variables.

@@

The resulting plots can be seen in Figure~\ref{fig:results}.

@@

\noindent SHIP is part of the Community Medicine Research net of the University of Greifswald, Germany, which is funded by the Federal Ministry of Education and Research (grant no. 03ZIK012), the Ministry of Cultural Affairs as well as the Social Ministry of the Federal State of Mecklenburg-West Pomerania. Whole-body MR imaging was supported by a joint grant from Siemens Healthcare, Erlangen, Germany and the Federal State of Mecklenburg-Vorpommern. The University of Greifswald is a member of the ‘Centre of Knowledge Interchange’ program of the Siemens AG. This work was supported by the DFG Priority Program 1335: Scalable Visual Analytics. This work was supported by the federal state of Saxony-Anhalt under grant number 'I 60' within the Forschungscampus STIMULATE.
